TBD

### 2016-10-17 paper.tex
started to improve least squares section

\section{Least Squares}
Redundant calibration can be achieved by solving the following optimization problem
\begin{equation}
\label{eq:red_least_squares}
\min_{\bz} \|\br\| = \min_{\bz} \|\bd - \bv(\bz)\|, 
\end{equation}
where $\bz = [\bg,\by]^T$. Eq.~\eqref{eq:red_least_squares} is a nonlinear least squares problem.

The most standard way of solving a general least squares problem is to use a gradient type of minimization algorithm whose main purpose is to find the model parameters that 
minimizes the difference between the observed and model data. In this paper we will be focusing on the following gradient minimization algorithms: Gauss-Newton and Levenberg-Marquardt (cite LM here). For the redundant calibration problem in Eq.~\eqref{eq:red_least_squares} $\bd$, which is the corrupted observed visibilities, is the observed data,
while $\bv$, which is the predicted visibilities, represents the model data.\footnote{In this paper we use the same symbol to denote predicted visibilities and true observed visibilities as it
is trivial to distinguish which one is implied from the context.}

@@

Recently Kreutz-Delgado and Sorber proposed an alternative strategy, which involves the use of Wirtinger calculus (Wirtinger 1927). The Wirtinger derivatives 
are defined to be 
\begin{align}
\frac{\partial}{\partial z} &= \frac{1}{2}\left ( \frac{\partial}{\partial x} -  i \frac{\partial}{\partial y} \right ),&\frac{\partial}{\partial \conj{z}} &= \frac{1}{2}\left ( \frac{\partial}{\partial x} +  i \frac{\partial}{\partial y} \right ). 
\end{align}
Using the above definitions we can now easily compute the following:
\begin{align}
\frac{\partial z}{\partial z} & = 1, & \frac{\partial \conj{z}}{\partial z}&=0, & \frac{\partial z}{\partial \conj{z}} & = 0, & \frac{\partial \conj{z}}{\partial \conj{z}}&=1.
\end{align}

\citet{Smirnov2015} recently proposed to use this Wirtinger framework instead of the classic real and imaginary approach to perform normal calibration. We will now show
that the Wirtinger framework can also be applied to redundant calibration. Analogous to \cite{Smirnov2015}, we recast Eq.~\eqref{eq:red_least_squares} to 
\begin{equation}
\label{eq:red_least_squares_complex}
\min_{\breve{\bz}} \|\breve{\br}\| = \min_{\breve{\bz}} \|\breve{\bd} - \breve{\bv}(\breve{\bz})\|, 
\end{equation}
where $\breve{\bz} = [\bz,\conj{\bz}]^T$, $\breve{\bd} = [\bd,\conj{\bd}]^T$, $\breve{\bv} = [\bv,\conj{\bv}]$. Eq.~\eqref{eq:red_least_squares_complex} is the augmented counterpart of Eq.~\eqref{eq:red_least_squares}.
If we use the Wirtinger derivative instead of the classic notion of a derivative to define the gradient operator then 
$\bv$ becomes analytic in $\bz$ and $\conj{\bz}$ as a whole. The fact that $\bv$ is now analytic in its argument has the immediate consequence that it becomes possible to use the Gauss-Newton
and the Levenberg-Marquardt algorithm to solve Eq.~\eqref{eq:red_least_squares_complex} \citep{Smirnov2015}.

>>>>

\section{Least Squares}
The method of nonlinear least squares is tanatamount to solving the following optimization problem  
\begin{equation}
\label{eq:red_least_squares}
\min_{\bz} \Lambda(\bz) = \min_{\bz} \|\br\|_F^2 = \min_{\bz} \|\bd - \bv(\bz)\|_F^2, 
\end{equation}
where $\Lambda$ is known as the objective function, $\br$ is the residual vector, $\bd$ is the observed data vector, $\bv$ is the model data vector and $\bz$ is the solution which minimizes Eq.~\eqref{eq:red_least_squares}.
The main objective of least squares is to find the model parameters which minimizes the squared difference between the observed data and the model. Moreover, $\|*\|_F$ denotes the 
Frobenius norm.

The most standard way of solving Eq.~\eqref{eq:red_least_squares} is to use a gradient type of minimization algorithm. In this paper we will be focusing on the following gradient minimization algorithms: Gauss-Newton and Levenberg-Marquardt \citep{Levenberg1944,Marquardt1963}.

@@

Recently, \citet{Sorber2012} proposed an alternative strategy, which involves the use of Wirtinger calculus \citep{Wirtinger1927}. The Wirtinger derivatives 
are defined to be 
\begin{align}
\frac{\partial}{\partial z} &= \frac{1}{2}\left ( \frac{\partial}{\partial x} -  i \frac{\partial}{\partial y} \right ),&\frac{\partial}{\partial \conj{z}} &= \frac{1}{2}\left ( \frac{\partial}{\partial x} +  i \frac{\partial}{\partial y} \right ). 
\end{align}
Using the above definitions we can now easily compute the following:
\begin{align}
\frac{\partial z}{\partial z} & = 1, & \frac{\partial \conj{z}}{\partial z}&=0, & \frac{\partial z}{\partial \conj{z}} & = 0, & \frac{\partial \conj{z}}{\partial \conj{z}}&=1.
\end{align}

\subsection{Redundant Calibration}
\citet{Smirnov2015} recently proposed to use this Wirtinger framework instead of the classic real and imaginary approach to perform normal calibration. We will now show
that the Wirtinger framework can also be applied to redundant calibration.

For the redundant calibration problem in Eq.~\eqref{eq:red_least_squares} $\bd$, which is the corrupted observed visibilities, is the observed data,
while $\bv$, which is the predicted visibilities, represents the model data.\footnote{In this paper we use the same symbol to denote predicted visibilities and true observed visibilities as it
is trivial to distinguish which one is implied from the context.}

 Analogous to \cite{Smirnov2015}, we recast Eq.~\eqref{eq:red_least_squares} to 
\begin{equation}
\label{eq:red_least_squares_complex}
\min_{\breve{\bz}} \|\breve{\br}\| = \min_{\breve{\bz}} \|\breve{\bd} - \breve{\bv}(\breve{\bz})\|, 
\end{equation}
where $\breve{\bz} = [\bz,\conj{\bz}]^T$, $\breve{\bd} = [\bd,\conj{\bd}]^T$, $\breve{\bv} = [\bv,\conj{\bv}]$. Eq.~\eqref{eq:red_least_squares_complex} is the augmented counterpart of Eq.~\eqref{eq:red_least_squares}.
If we use the Wirtinger derivative instead of the classic notion of a derivative to define the gradient operator then 
$\bv$ becomes analytic in $\bz$ and $\conj{\bz}$ as a whole. The fact that $\bv$ is now analytic in its argument has the immediate consequence that it becomes possible to use the Gauss-Newton
and the Levenberg-Marquardt algorithm to solve Eq.~\eqref{eq:red_least_squares_complex} \citep{Smirnov2015}.
